Supplementary Information

### 2020-10-08 writing/transect_supplement.Rmd
improve read quality plot

```{r qual-check, fig.cap = "(ref:qual-check-s). (ref:qual-check)", fig.scap = "(ref:qual-check-s)"}
ggpubr::ggarrange(
  readd(erate_plot),
  readd(eexp_plot),
  ncol = 1,
  common.legend = TRUE,
  legend = "bottom",
  labels = "auto"
)
```

>>>>

```{r qual-check, fig.cap = "(ref:qual-check-s). (ref:qual-check)", fig.scap = "(ref:qual-check-s)",fig.height=6}
ggpubr::ggarrange(
  readd(erate_plot),
  readd(eexp_plot),
  readd(eexp_region_plot),
  ncol = 1,
  # common.legend = TRUE,
  # legend = "bottom",
  labels = "auto"
)
```
